### 2024-03-05 doc/15yrsChange.Rmd
Update 15yrsChange.Rmd

## Paragraph discussing broad trend of biomass stock decrease (Figure 2) & net change in biomass & differences among regions in the plot 
For the first time at the Front Royal ForestGEO site, C stocks have decreased since the last census (Figure 2). From 2018 to 2023, whole-plot C stocks have decreased from **"X to X"** Mg C/ha. Both low nuisance regions show similar decreases in C stocks going from **"X to X"** and **"X to X"** Mg C/ha respectively. The magnitude of the C stock decrease in the high deer high nuisance area from 2018 to 2023 is larger, going from **"X to X"** Mg C/ha. C stock decrease **is related to/ is explained by** above ground net woody production. In the first two census intervals, 2008 to 2013 and 2013 to 2018, there were positive C fluxes **VALUES?** and for the 2018 to 2023 interval there was a negative C flux of **VALUE Mg C/ha/year** (Figure 3a).

@@

>>>>

## Paragraph discussing broad trend of biomass stock decrease (Figure 2) & net change in biomass & differences among regions in the plot 
For the first time at the Front Royal ForestGEO site, whole-plot C stocks have decreased since the last census (Figure 2). From 2018 to 2023, whole-plot C stocks have decreased from **"X to X"** Mg C/ha. Both low-nuisance regions show similar decreases in C stocks going from **"X to X"** and **"X to X"** Mg C/ha, respectively. In the high deer high nuisance regions C stocks have decreased for the past two censuses, with a higher magnitude decrease of **"X to X"** Mg C/ha from 2018 to 2023. C stock decrease **is related to/ is explained by** above ground net biomass change. In the first two census intervals, 2008 to 2013 and 2013 to 2018, there were positive C fluxes, but for the 2018 to 2023 interval there was a negative C flux of **VALUE** Mg C/ha/year (Figure 3a).

@@

Woody mortality was the largest driver of the negative trend in biomass, and certain species were responsible for higher levels of mortality. Fraxinus americana had the highest abovegroung woody mortality rates of any species present on the plot, peaking at **VALUE** Mg C/ha/year lost in *2020* , and **VALUE** Mg C/ha/year lost in 2022 (Figure 4). Quercus velutina contributed the second-highest levels of mortality, losing **VALUE** Mg C/ha/year in 2022. Quercus rubra, Carya species, Quercus prinus, Quercus alba, and Liriodendron tulipifera were all significant contributors as well.
